---
title: "Color quantization"
author: "Márcio Martins"
date: "11 de Maio de 2018"
output: 
  github_document:
    dev: "png"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./scripts/helper_functions.R")
library(scales)
library(jpeg)
```

This is a small personnal project inspired on some blog posts (see below). The main goal is to create a function that takes a raster image as input and returns a color palette that best represents that image. While reading the posts about how the author of the PaletteR package tries to not only maximize how well a palette represents an image, but also make sure that colors are as distinguishable as possible, I decided to read up on how color quantization is normally performed. One of the most widely mentioned (and simpler) algorithms was called median cut. It seemed relatively simple and I decided to try and implement in in R.


Blog posts that lead to this project:
http://www.milanor.net/blog/build-color-palette-from-image-with-paletter/
https://datascienceplus.com/how-to-use-paletter-to-automagically-build-palettes-from-pictures/

Median cut algorithm:
https://en.wikipedia.org/wiki/Median_cut

This implementation is of the most basic version of the algorithm, meaning color palettes will always have a number of colors that is base 2.

Here is the result:

```{r images}
